---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidyklips

<!-- badges: start -->
<!-- badges: end -->

tidyklips is an R package that allows users to interface with the Korea Labor Institute's yearly KLIPS(Korea Labor & Income Panel Study) and return tidyverse-ready data frames, optionally with time-series features included.


## Installation

You can install the development version of tidyklips from [GitHub](https://github.com/cheongchoi/tidyklips) with:

```{r}
# install from CRAN
install.packages("tidyklips")

# install dev version
devtools::install_github("cheongchoi/tidyklips")

```

## Example

This is a basic example which shows you how to obain a dataframe file from KLIPS:

```{r eval=FALSE}
# first, you need to download the .zip file from KLIPS homepage <https://www.kli.re.kr/klips>.
# second, you need to unzip that file.
# third, you need to remember the folder path.

library(tidyklips)
library(dplyr)
library(magrittr)
path <- system.file("extdata", package = "tidyklips")
df <- getpklips(path = mypath, year = 2023, datatype = "stata") 

# you need to adjust the path. 
# This code is equivalent to the following code

df <- klips26p
df2 <- df 
    dplyr::group_by(gender) %>%
    dplyr::summarise(count = dplyr::n()) %>%
    dplyr::mutate(proportion = count / sum(count))
```


```{r eval=FALSE}
summary(df)

```
```{r eval=FALSE}
summary(df2)
```

```{r pressure, echo = FALSE, eval=FALSE}
barplot(df2$proportion~as.factor(df2$gender))
```

